Cryptographic assurance of secrecy and fairness in voting

### 2012-12-06 paper/paper.tex
Rework brief section on voter involvement

It is important to note -- and the Helios researchers note this -- that this hinges on active
involvement from the community.

>>>>

It is worth noting that without active participation on the part of the voters, none of these
schemes provide significant benefit. Only if some voters actually \emph{do} audit the election
processes is there any guarantee that the election was fair.

The creators of Helios note this fact, and it is reflected in their work, as the system makes at
least recording verification an obvious and easy process.
